\documentclass[10pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[left=3cm,right=3cm,top=4cm,bottom=3cm]{geometry}

\address{Andrzej Strzelba\\Kwiatowa 4 Street\\
66-666 Hel, Poland} 
\signature{Andrzej Strzelba} 


\begin{document} 
\begin{letter}{Mr Rich\\Spaghetti 30 Street\\San Francisco, California 34678} 
\opening{Dear Sir or Madame,} 
 
I would like to apply to position Junior Babysitter Engineer. I found this job position offer on jobs.stackoverflow.com posted on 20 September 2005.

I am fresh graduate with passion and love towards children, animals and other living (or not) creatures. Basically I like everything that is breathing, it does not have to move neccessarily. I have attended numerous courses on Academy of Babysitting and Caring in Wroclaw and I have Professional Babycare Master Certificate, which I have acquired with honours from Andrzej Duda, President of Poland.

Babysitting your child would bring me huge joy and would cause huge step forward my plans on conquering the world.

Looking forward for accepting my position offer and hearing feedback from you.
\closing{Your Sincerely,} 
%\cc{Cclist} 
%\ps{adding a postscript} 
%\encl{list of enclosed material} 
\end{letter} 
\end{document}


% =============== STARE ===================



\iffalse
\documentclass[12pt,a4paper,oneside]{letter}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[left=3cm,right=3cm,top=4cm,bottom=3cm]{geometry}

\signature{}
\author{Tomasz Mączkowski}


\begin{document}
\hspace{5pt}
\begin{flushleft}
Mr Rich\\
Spaghetti 30 Steet\\
San Francisco, California 34653\\
\end{flushleft}

\hspace{5pt}
\begin{flushright}
Andrzej Strzelba\\
Kwiatowa 4 Street\\
66-666 Hel, Poland\\
Szczecin, \today
\end{flushright}

\hspace{5pt}
\begin{flushleft}
Dear Sir,
\end{flushleft}
I would like to apply to position Junior Babysitter Engineer. I found this job position offer on jobs.stackoverflow.com posted on 20 September 2005.

I am fresh graduate with passion and love towards children, animals and other living (or not) creatures. Basically I like everything that is breathing, it does not have to move neccessarily. I have attended numerous courses on Academy of Babysitting and Caring in Wroclaw and I have Professional Babycare Master Certificate, which I have acquired with honours from Andrzej Duda, President of Poland.

Babysitting your child would bring me huge joy and 

\end{document}
\endif